BERT Model Compression and Weight Sharing

### 2019-05-12 paper/paper.tex
Change table formatting to be more readable
Fix first bullet point
Add curious training curves into paper.tex

\begin{abstract}
\raggedright
  \begin{itemize}
  \item We apply model compression results to fine-tuned BERT on multiclass
  classification problems.
  \item Knowledge distillation and DeepTwist-based compression techniques give
  us moderate compression benefits for a commensurate decrease in model
  performance.
  \item We achieve our most compelling results from employing the DeepTwist
  framework to share weights across BERT models fine-tuned for different tasks.
  \item Our work demonstrates most weights need not change in the fine-tuning
  process.
%   \item This document describes the expected style, structure, and rough
%   proportions for your final project write-up.
%   \item While you are free to break from this structure, consider it a strong
%   prior for our expectations of the final report.
%   \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
%   in this format. While you can include supplementary material, it will not be
%   factored into the grading process. It is your responsibility to convey the
%   main contributions of the work in the length given.
  \end{itemize}

@@

\input{../tabs/deeptwist_table.tex}

@@

As expected, pruning a higher proportion of the weights decreases performance,
but we are happily surprised at the relatively low magnitude of this effect even
at high prune rates. Pruning with a global threshold rather than in a
stratified way produces distinctly worse results. We suspect this is due to
weights in different layers having different magnitudes, making a global
threshold have an undue effect on layers whose weights tend to be smaller. We
confirm this heterogeneity in 
% TODO: include box-plots of weights

@@

>>>>

\begin{abstract}
\raggedright
  \begin{itemize}
  \item We apply model compression techniques to fine-tuned BERT on multiclass
  classification problems.
  \item Knowledge distillation and DeepTwist-based compression techniques give
  us moderate compression benefits for a commensurate decrease in model
  performance.
  \item We achieve our most compelling results from employing the DeepTwist
  framework to share weights across BERT models fine-tuned for different tasks.
  \item Our work demonstrates most weights need not change in the fine-tuning
  process.
%   \item This document describes the expected style, structure, and rough
%   proportions for your final project write-up.
%   \item While you are free to break from this structure, consider it a strong
%   prior for our expectations of the final report.
%   \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
%   in this format. While you can include supplementary material, it will not be
%   factored into the grading process. It is your responsibility to convey the
%   main contributions of the work in the length given.
  \end{itemize}

@@

\input{../tabs/hierarchical_deeptwist_table.tex}

@@

As expected, pruning a higher proportion of the weights decreases performance,
but we are happily surprised at the relatively low magnitude of this effect even
at high prune rates. Pruning with a global threshold rather than in a
stratified way produces distinctly worse results. We suspect this is due to
weights in different layers having different magnitudes, making a global
threshold have an undue effect on layers whose weights tend to be smaller. We
confirm this heterogeneity in \cref{fig:weightsbylayer}.

\begin{figure}[htb]
\centering
\includegraphics[width=.5\textwidth]{../figs/value_by_layer.pdf}
\caption{Weight distributions for five most/least variable layers}
\label{fig:weightsbylayer}
\end{figure}

@@

\begin{figure*}[tb]
\centering
\includegraphics{../figs/kd_lstm_training.png}
\caption{Training loss (left), val. loss (middle), and val. accuracy
(right) for LSTM KD}
\label{fig:<+label+>}
\end{figure*}<++>
